\tool: Programmable, Efficient, and Scalable \\ Secure Two-Party Computation for Machine Learning

### 2018-05-08 ccs/intro.tex
tweaks to intro

This paper presents \tool\footnote{Read as ``easy peasy'',
stands for Easy 2 Party Computation.}, the first
``cryptographic-cost aware'' framework that generates efficient and
scalable \mpc protocols from high-level programs devoid of any
cryptographic details. 
The generated protocols use combinations of
arithmetic and boolean circuits that introduce unique compilation challenges.
Standard compilers do not attempt to reason about or insert non-trivial type casts
and require the programmers to perform them explicitly. \aseem{This
last sentence and the bit about unique compilation challenges seems
unnecessary to me. Compilers do insert type casts automatically. Also
at this point in the paper the words ``type casts'' don't mean much.}
We back \tool with formal semantics that enable the compiler to
insert type conversions between boolean and arithmetic components
while maintaining provable correctness, security, and
efficiency. \aseem{Provable efficiency? Perhaps provable should
be rescoped. And again, type conversions may not be clear at this
point. I would simply say that EzPC inserts inter-conversion gates
automatically. It is backed by a formal model and provides
provable correctness and security, and efficiency.}
The automatically generated protocols have performance comparable to
or better than the custom, specialized
protocols from previous works~\cite{shafindss,wu,minionn,secureml,cryptonets,valeriaMatrix}.
In fact, these papers (and others) cite the inefficiency of generic \mpc as the major motivation
behind the design of specialized protocols. Using \tool, we empirically  demonstrate
that generic \mpc implementations are much more efficient than what they were believed to be. 
 %(up to a factor of 19x in our
%experiments, depending on the functionality) \nc{I added this but I
%  guess we are saying it many times, but might be nice to highlight
%  perf early no?} \aseem{My rationale was to save the numbers for
%  Evaluation summary and remain high-level here.} 
Below we describe
the salient features of \tool.

>>>>

This paper presents \tool\footnote{Read as ``easy peasy'',
stands for Easy 2 Party Computation.}, the first
``cryptographic-cost aware'' compiler that generates efficient and
scalable \mpc protocols using combinations of
arithmetic and boolean circuits. \tool is backed by a formal model
that enables it to choose arithmetic or boolean representations for
different parts of
the program, while automatically inserting inter-conversion gates as
necessary. In addition to guiding the compiler, the formal model also
provides strong correctness and
security theorems. Our comprehensive evaluation shows that the
automatically generated protocols have performance comparable to
or better than the custom, specialized
protocols from previous works~\cite{shafindss,wu,minionn,secureml,cryptonets,valeriaMatrix}.
In fact, these papers (and others) cite the inefficiency of generic \mpc as the major motivation
behind the design of specialized protocols. Using \tool, we empirically  demonstrate
that generic \mpc implementations are much more efficient than what they were believed to be. 
Below we describe
the salient features of \tool.

%% that introduce unique compilation challenges.
%% Standard compilers do not attempt to reason about or insert non-trivial type casts
%% and require the programmers to perform them explicitly. \aseem{This
%% last sentence and the bit about unique compilation challenges seems
%% unnecessary to me. Compilers do insert type casts automatically. Also
%% at this point in the paper the words ``type casts'' don't mean much.}
%% We back \tool with formal semantics that enable the compiler to
%% insert type conversions between boolean and arithmetic components
%% while maintaining provable correctness, security, and
%% efficiency. \aseem{Provable efficiency? Perhaps provable should
%% be rescoped. And again, type conversions may not be clear at this
%% point. I would simply say that EzPC inserts inter-conversion gates
%% automatically. It is backed by a formal model and provides
%% provable correctness and security, and efficiency.}

%% This paper presents \tool\footnote{Read as ``easy peasy'',
%% stands for Easy 2 Party Computation.}, the first
%% ``cryptographic-cost aware'' framework that generates efficient and
%% scalable \mpc protocols from high-level programs devoid of any
%% cryptographic details. 
%% The generated protocols use combinations of
%% arithmetic and boolean circuits that introduce unique compilation challenges.
%% Standard compilers do not attempt to reason about or insert non-trivial type casts
%% and require the programmers to perform them explicitly. \aseem{This
%% last sentence and the bit about unique compilation challenges seems
%% unnecessary to me. Compilers do insert type casts automatically. Also
%% at this point in the paper the words ``type casts'' don't mean much.}
%% We back \tool with formal semantics that enable the compiler to
%% insert type conversions between boolean and arithmetic components
%% while maintaining provable correctness, security, and
%% efficiency. \aseem{Provable efficiency? Perhaps provable should
%% be rescoped. And again, type conversions may not be clear at this
%% point. I would simply say that EzPC inserts inter-conversion gates
%% automatically. It is backed by a formal model and provides
%% provable correctness and security, and efficiency.}
%% The automatically generated protocols have performance comparable to
%% or better than the custom, specialized
%% protocols from previous works~\cite{shafindss,wu,minionn,secureml,cryptonets,valeriaMatrix}.
%% In fact, these papers (and others) cite the inefficiency of generic \mpc as the major motivation
%% behind the design of specialized protocols. Using \tool, we empirically  demonstrate
%% that generic \mpc implementations are much more efficient than what they were believed to be. 
%%  %(up to a factor of 19x in our
%% %experiments, depending on the functionality) \nc{I added this but I
%% %  guess we are saying it many times, but might be nice to highlight
%% %  perf early no?} \aseem{My rationale was to save the numbers for
%% %  Evaluation summary and remain high-level here.} 
%% Below we describe
%% the salient features of \tool.
